\huge \textbf{Parameter Forecasts From CMB Lensing and Galaxy Lensing Power- and Bispectra}

### 2025-05-02 paper/paper_draft.tex
added tables

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/param_constraints_tight.pdf}
    \caption{Constraints for $H_0$, $\sigma_8$, and $\Omega_m$ for different combinations of weak lensing spectra. Valid for ``stage 4'' experiments. We use $l_{\max}=2000$. The confidence ellipses are for $1\sigma$ certainty. The standard deviation of each Gaussian is given explicitly in the top left corners of the diagonal plots.}
    \label{fig:paramconstraintstight}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/param_constraints_all.pdf}
    \caption{Same as Fig. \ref{fig:paramconstraintstight}, except comparing constraints for all parameters of our $\Lambda$CDM cosmology.}
    \label{fig:paramconstraintsall}
\end{figure}

@@

To test the accuracy, we vary $h$ by $\pm 5\%$ and $\pm 10\%$ and plot the relative change in the derivative of the equilateral bispectrum in figure \ref{fig:deraccuracy}. As long as numerical noise doesn't dominate, it can be shown that the relative error in our approximation is approximately 5 times the relative difference that taking $h \rightarrow h(1 \pm 0.1)$ leads to. We thus conclude that, based on this test, the derivatives are almost always computed with up to one percent of error.

\begin{figure}[t]
    \centering
    \includegraphics[height=\textheight]{/Users/jonasfrugte/Desktop/Research_Project/fisher_calc_weak_lensing/code/plots/derivative_accuracy.png}
    \caption{Central difference approximation of derivative of equilateral CMB weak lensing bispectrum for differences as specified in table \ref{tab:cosmo-params-diff} as well as for differences $5\%$ and $10\%$ larger and smaller.}
    \label{fig:deraccuracy}
\end{figure}

>>>>

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par            &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$          &                41.0 &              1.9 &                 7.4 &                 4.8 &                       0.7 \\
         $\Omega_b h^2$ &               109.8 &             18.4 &                10.1 &                17.3 &                       7.1 \\
         $\Omega_c h^2$ &                58.3 &              2.4 &                 2.2 &                 2.7 &                       1.1 \\
         $n_s$          &                11.4 &              1.9 &                 1.8 &                 3.2 &                       1.0 \\
         $m_\nu$        &               603.3 &            373.9 &               216.3 &               260.1 &                     102.3 \\
         $A_s$          &                39.1 &              7.0 &                 3.4 &                 7.8 &                       2.4 \\
         $w_0$          &                46.1 &              3.1 &                18.3 &                12.7 &                       1.6 \\
        \hline
    \end{tabular}
\caption{Parameter constraints in percentage of the fiducial values for different combinations of weak lensing information.}
\label{tab:paramconstraintsall}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/param_constraints_all.pdf}
    \caption{Same as Fig. \ref{fig:paramconstraintstight}, except comparing constraints for all parameters of our $\Lambda$CDM cosmology.}
    \label{fig:paramconstraintsall}
\end{figure}

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par        &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$      &        3.3022621043 &     0.9658765234 &        0.1360204496 &        0.6433515918 &              0.1173950908 \\
         $\sigma_8$ &        0.0000000178 &     0.0000000148 &        0.0000000023 &        0.0000000122 &              0.0000000020 \\
         $\Omega_m$ &        0.4126866976 &     0.2388283763 &        0.1579156300 &        0.1996632391 &              0.1122269336 \\
        \hline
    \end{tabular}
\caption{Same as table \ref{tab:paramconstraintsall}, except for a smaller selection of parameters well constrained by lensing.}
\label{tab:paramconstraintstight}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/param_constraints_tight.pdf}
    \caption{Constraints for $H_0$, $\sigma_8$, and $\Omega_m$ for different combinations of weak lensing spectra. Valid for ``stage 4'' experiments. We use $l_{\max}=2000$. The confidence ellipses are for $1\sigma$ certainty. The standard deviation of each Gaussian is given explicitly in the top left corners of the diagonal plots.}
    \label{fig:paramconstraintstight}
\end{figure}

@@

To test the accuracy, we vary $h$ by $\pm 5\%$ and $\pm 10\%$ and plot the relative change in the derivative of the equilateral bispectrum in figure \ref{fig:deraccuracy}. As long as numerical noise doesn't dominate, it can be shown that the relative error in our approximation is approximately 5 times the relative difference that taking $h \rightarrow h(1 \pm 0.1)$ leads to. We thus conclude that, based on this test, the derivatives are almost always computed with up to one percent of error. The exception is the derivative with respect to neutrino masses, which introduces a larger error.

\begin{figure}[t]
    \centering
    \includegraphics[height=\textheight]{/Users/jonasfrugte/Desktop/Research_Project/fisher_calc_weak_lensing/code/plots/derivative_accuracy.png}
    \caption{Central difference approximation of derivative of equilateral CMB weak lensing bispectrum (left) and powerspectrum (right) for differences as specified in table \ref{tab:cosmo-params-diff} as well as for differences $5\%$ and $10\%$ larger and smaller.}
    \label{fig:deraccuracy}
\end{figure}
